---
title: "Experiment 4"
author: "Darrell Penta"
date: "April 15, 2015"
output: html_document
---

***
## I. EXP OVERVIEW
### a. What you did 

* You saw a whole punch of letter string, one after another
  * _Primes_ and _Targets_, both of which had __word__ and __non-word__ versions
* You just answered yes or no
* There was also a delay in the timing between the presentation of the prime and the target
* For word-word target-prime pairings, half of the words share an association

IV | Level
---|-----
Prime | Word, Non-word
Targets | Word, Non-word
ISI (inter-stimulus interval) | 50ms, 100ms, 200, 350, 500
Association | association (half the words), not-associated

DV | Level
----|-----
RT | How quickly do you decide it's a word
Trials with no key press set to 0

Accuracy | Were you right
whether the yes no key press matched target type

### b. Experimental questions
* _Question here is about timing of information flow in the system_
    + This is an examination of activition system view of long-term memory (LTM) in which activation is a quantity tha can spread around
    +  Example:
    Seeing __EMERALD__ should activate your knowledge of emerald and things related to it, like __DIAMOND__
* The system tracks these realtionships and uses them during day-to-day operations


    
* _How is knowledge organized in long-term memory?_ 

***

## II. BACKGROUND

<div style="border: 1px solid #000000; padding: 5px">

### Activitation system (a. Theory 1)
* _Nodes_ which represent something/perice of knowledge that can collect activation
  * Activation happens quickly, and nodes can activate/deactive quickly
* _Connections/Links_ between nodes, with activation spreading through the links.
    + The system change over time (you can learn new things)
* _Nodes_ have 2 activation levels:
    + Resting level (non-zero level, but low) is the baseline
    + current level is dynamic, changes based on things like are you thinking about that word or reading that word, etc
    + Current level and Resting level can be = and presumably are most of the time
* _Connections_ have weights/strenghts:
    + How much information spread at a given moment
    + Exmample: Due to connection weights, more likely that _EMERALD_ spreads activation to _DIAMOND_, but less to _GREEN_
    + weights set by prior experience
    + can change over time by learning based on experience
* Assocation is not the only kind of relationship

Associative words speed up/prime activation 
* Can be one way

Ratcliff & McKoon
Can mess around with episodic memory
People learn: "The doctor kissed the lawyer"
They gave people words in tests where the target is something like lawyer, and the preceding word was either from the sentence they learned or not




PARAMETRIC EXPERIMENT
We're looking at a specific parameter of the system (namely, how quickly activation can spread/timing of activation spread)


Unassociated pairing are the baseline.
Associated should be faster than baseline
Looking at whether activation has spread to the target or not
Look at:
short ISIs tell us how quickly activation spreads
long ISIs tell us now long activation remains



<div style="background:#ccffff;border: 1px solid #000000; padding: 5px; margin: 10px 0px 10px 25px">
#### Notes from (Readings)  
#### Theory 1
* point 1 templates are holistic and unanylzed
    * subpoint 1
##### Experimenter (year)    
* Notes
* Notes
</div>

<div style="border: 1px solid #000000; padding: 5px">
### ( b. Theory 2)
</div>

<div style="background:#ccffff;border: 1px solid #000000; padding: 5px;  margin: 10px 0px 10px 25px">
#### Notes from (Readings)
#### Theory 2
</div>



*** 
<div style="background:#fff0f5; border: 2px solid #990000">
## Abstract (10) 
* Describe 

## Intro (20)
* General 
* Brief description of 
* Predictions of 

</div>

***
<div style="border: 1px solid #000000; padding: 5px">
## II. METHOD

### Participants:
16 NU Undergrads

### Apparatus:
MicroExperimental lab sortware running DOS

### Materials:
Notes
* non-words were pronouncable
* associated and unassociated word targets were match for length and frequenc
### Procedure:
overall:
choice of Y/N keys
instructions
4 practice trials
160 exp trials
15 minutes
indiv
spacebar
-prime
isi
target
y/n





#### Overall: 
Notes

#### Individual: 
Notes

### Design:
Notes
#### IVS
1. IV1
    * Level
2. IV2
    * All IVs manipulated within Ps

#### DVs
1. DV1
</div>

<div style="background:#fff0f5;border: 2px solid #990000">
## Method

### Participants (2)
  * 

### Apparatus (2)
  * 

### Materials (3)

### Procedure (4)
* notes
* notes

#### Indiv trial structure
* notes
* notes
#### Overall expt:  
* notes
* notes

### Design (4)
 * notes
 * notes
</div>



***

## Results
* notes
* notes

### 1. Which Analyses

#### Collapsing

* Collapsed over 
* Collapsed over 


#### Results

* We did not 
* We _DID_ find 

```{r, echo=FALSE, error=FALSE, warning=FALSE}
library(ggplot2)

class.ano <- data.frame(
letter  = factor(c("Q","Q","Z","Z")),
context = factor(c("Rnd","Ang","Rnd","Ang"), levels=c("Rnd","Ang")),
RT    = c(4864, 3807, 3732, 4425))
```

```{r, echo=FALSE}

# Basic line graph with points
ano.pl <- ggplot(data=class.ano, aes(x=context, y=RT, group=letter, color=letter)) +
    geom_line() +
    geom_point() +
    theme_bw() +
    xlab("Context") + ylab("Reaction Time (ms)") +
    ggtitle("Reaction time as a function of context and target letter")

ano.pl + scale_shape_discrete(name="Target Letter") + scale_color_discrete(name="Target Letter")

```


 <div style="background:#fff0f5;border: 2px solid #990000">
## Results (15)

* dropped 
Analyses factorial  analysis: 
  * collapsing; 
  * describe pattern;
  * refer to fig; 
  
</div>
***
Feature Theory (Talked about in Intro):

* Knows and cares about _amount_ of overlap
* computes this overlap by comparing number of features shared (e.g., Q vs. D): (, ), ~ vs. ), |
* more shared features means slower reaction times
  + Q<sub>ROUND</sub> > Q<sub>ANGULAR</sub>
  + Z<sub>ROUND</sub> <= Z<sub>ANGULAR</sub>
  
# Discussion
* Template theory doesn't have a way of talking about anything other than overall overlap
* It doesn't say anything about combinations (It shouldn't know that a Q overlapped with a D has some overlap with a Q overlapped with a V)
* Predicts no interaction between target and context
* Specific pattern of results matches the feature theory predictions
* WE can define a specific set of features for the relevant letters, and we can define a function that computes amount of overlap
    + we have a set of features counted up (see table)

#### Calculating % overlap:    
 
Eq:  (% overlap = # features matching / # of features in context  
<div stlye="width:50%">
Target x context|Match/Total|Percentage
----------------|-----------|----------
Q<sub>ROUND</sub>| 2/5| 40
Q<sub>ANGULAR</sub>| 1/8 | 12.5
Z<sub>ROUND</sub> |0/5| 0
Z<sub>ANGULAR</sub>| 1/8 |12.5
</div>    
Because we don't see a perfect match in the computations and the results, there's more to the story 
-potential problem: we're not considering how many times each of the features appear, we might want to adjust the function to weight features

We found an interaction, which fits with the feature theory but does not fit with the template theory
-What might you do to the template theory to explain the pattern?
    

<div style="background:#fff0f5;border: 2px solid #990000">

## Discussion (15)

* compare results w/predictions (recap predictions if needed)
  * no effect of target or context, compatible w/either theory, but interaction inconsistent w/Template and consistent w/Feature; 
* explain meaning of slope (time to scan a row) [and mention goodness of fit to regression line for earlier vs later rows (optional; should be here or in Results; nothing to do for Spr2015)];

* discuss augmentation of Template;

* discuss Structural Feature Theory (if not covered in Intro);

* cover detailed feature theory and quantitative predictions here, relating to ANOVA results, etc. (some flexibility about how much they say about quantitative feature predictions, but they should present a feature-breakdown and work out % of overlap, relating to results, at a minimum); 

* usual general issues & extensions


## FIGS AND TABLES (15)

graph for RT by target and context

graph for RT by row, including regression line

check axis labels, axis tick spacing, graph titles, etc.

</div>



***
### READINGS:
* Levy, C.M., & Ransdell, S. E. (1988). _Laboratory in cognition and perception (2nd ed.)._ Iowa City: CONDUIT, Univ. of Iowa.
* Neisser, U. (1967) _Cognitive Psychology_. Englewood Cliffs, NJ: Prentice-Hall. [Neisser (1967)](http://infinitychallenge.com/articles/Neisser_1967.pdf)
* Reed, S.K. (1998) _Cognition: Theory and appliciations_. Pacific Grove, CA: Brooks/Cole. [Reed (1988)](http://infinitychallenge.com/articles/Reed_1988.pdf)
* Schneider, W. (1988) Micro Experimental Laboratory: An integrated system for IBM PC compatibles: _Behavior Research Methods, Instruments, & Computers, 20_, 206-217.

